---
title: Final Project
author: Team Red
output: github_document
---

## Summary

This project is an exploratory examination of US housing data. This data consists of several elements such as listing price, building type, garage area, and etc. The purpose of this project was to examine how some variables such as lot area affects the sales price of houses. Additionally, we examined the relationships formed by variables such as the relationship between houses listed and the quantity of their building type that of which was listed. The team used various visualization techniques to examine
this data.

Some challenges arose when dissecting the data provided, one of which was determining which variables to focus on as each listing has various details. Due to the amount of variables some have been omitted from our research in order to save time and simplify the project. Other challenges include deciphering what models we wish to make, due to the abundance of data, in order to better discover and express what patterns or relationships that can be formed from the US Housing dataset.

The first three graphs are a focus on the housing market’s composition of house styles and building type. For our purposes and as shown in the dataset, housing style describes the amount of stories that the house has, the most common being 1 story houses in the dataset. Building Type describes the type of building the house is; for example, a single-family detached house or a duplex. Notably Single-family detached houses were the most common with around 1250 units listed in the dataset. The first two graphs examine houses listed and their respective styles and building types. The third graph takes both house style and building type into consideration and shows us that the most commonly listed house was 1st story single family housings followed secondly by 2-story single family housings. While we may lack some data to prove this, it is a hint at the change of housing markets where households had at one time held multiple families and/or multiple generations. This could hint at a greater isolation of inhabitants, yet this is beyond the purview of our study.

The fourth and fifth graph are representations of house style and their relationships with the year that they were built and the year that they so happened to be sold. The following sixth graph is a representation of house style and sales price.

The seventh graph checks building type and compares it to sale price, similar to graph six.
The eighth graph is a representation of when the house was built and when it sold while also observing the price of those houses.

The last graph is a predictive graph of how lot area affects sales price and what years these houses were sold.

Should we continue this study or re-perform it we may choose to have a more structured plan on determining which variables should be examined and compose a more formal speculation of how these variables may interact with each other. It may have been in our best interest to include a glossary or a description of the variables not for the sake of observers, but for us who had to work attempting to understand the differences of building type and housing styles.

In conclusion, this research project provides a valuable insight into the relationship between various housing characteristics and the number of listings and sales. The team found that single-family detached homes were the most commonly listed and sold, while two-family conversions were the least frequently listed and sold. Additionally, 1 and 2 story houses were the most commonly built across all building types and the most commonly sold house styles.


```{r load-data, echo = FALSE}
testingdataset <- read.csv("/cloud/project/project-example-main/project-example-main/data/housing_train.csv")
```

## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Link to dataset: https://www.kaggle.com/datasets/gpandi007/usa-housing-dataset

Retrieval date: March 15, 2023

## References
Ganesh, 2018, USA Housing dataset, housing_train.csv, Ganesh, viewed 27 March 2023, <https://www.kaggle.com/datasets/gpandi007/usa-housing-dataset>.





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("readr")
library(readr)
library(ggplot2)

```

```{r measurments, echo=FALSE}

ggplot(data = testingdataset, mapping = aes(x = HouseStyle, fill = HouseStyle,)) + 
  geom_bar()+
  labs(title = "Houses Listed By Housing Style",
       x = "House Style",
       y = "# Houses Listed",
       ) 
```       
Bar Plot 1:
In this bar plot, we chose to examine the relationship between the houses listed and the house style. We found that 1 story houses were the most prevalent of those listed, followed by 2 story houses, while 2.5 story houses with a finished second level were the least likely to be listed.     
       
```{r measurments, echo=FALSE}

ggplot(data = testingdataset, mapping = aes(x = BldgType, fill = BldgType)) +
  geom_bar() +
  labs(title = "Houses Listed By Building Type",
       x = "Building Type",
       y = "# Houses listed",
       )
```
Bar Plot 2: 
In this bar plot we examine the relationship between the houses listed and the building type. According to the data, we found that single-family detached houses were by far the most common, with nearly 1250 listed. Townhouse end units come in second in terms of frequency among the listed houses, but are still far less common at about 125 listed. The least common building type listed was the two-family conversion (houses that were originally built as single-family), with approximately 35 listings.

```{r measurments, echo=FALSE}
ggplot(data = testingdataset, mapping = aes(BldgType, HouseStyle, color = BldgType)) + 
  geom_count()+
  labs(title = "Building Type & Style",
       x = "Building Type",
       y = "House Style",
       size = "Number of Listed Properties",
       color = "Building Type") 

```
Plot 3:
In this plot we examined the relationship between several variables: the house style, building type, and number of listings. The most common combination of house style and building type we found listed was the 1-story, single-family home, followed closely by the 2-story, single-family home. In general, we noticed that regardless of house style, single-family homes tended to outnumber all other building types. And, as established in the previous plot, two-family conversions were the least frequently listed houses, despite having a greater variety of house styles than the similarly uncommon townhomes. Altogether, this indicates that building type may play a more significant role than house style in terms of which house characteristics prospective homebuyers are prioritizing. 

```{r years}
p <- ggplot(testingdataset, aes(YearBuilt, HouseStyle)) + geom_point()

# Use vars() to supply faceting variables:
p + facet_wrap(vars(BldgType)) +
  labs(title = "Style of Houses Built grouped by Building Type (approx. 1860-2020)",
       x = "Year Built",
       y = "Style of House",
       )
```
Plot 4:
In these plots we examined the relationship between house style and year built for each building type. With regards to single-family homes, 2 story houses and 1.5 story houses with a finished second level seem to be the most consistently built homes since the late 1800s, with 1 story houses eventually exceeding their frequency after 1900. Two-family conversions, while never particularly common, were more prevalent prior to the 1970s, after which they stopped being built entirely. Duplexes, on the other hand, only started being built in (relatively) large numbers after 1940. Similarly, we found that townhomes, regardless of style or type, only started being built around the 70s. Additionally, across all building types, 1 and 2 story houses styles tended to be the most common.

```{r prices}
ggplot(testingdataset, aes(YrSold, fill = HouseStyle)) +
  geom_histogram() +
    labs(title = "Types of Houses Sold (2006-2010)",
         x = "Year Sold",
         y = " ",
       )
```
Plot 5:
In this graph we examined the relationship between the house style, the year sold, and the number of listings. Of the houses sold in any given year, 1 story homes were the most prevalent – usually consisting approximately 50% of the listings. On the other hand, 2.5 story homes tended to be among the least frequently listed.


```{r measurments, echo=FALSE}
ggplot(testingdataset, aes(x=BldgType, y=SalePrice, fill=BldgType)) +
  geom_boxplot() +
    labs(title = "Central Tendencies of Sale's Price based on Building Type",
         x = "Building Type",
         y = "Sale's Price ($)",
       ) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE, big.mark = ",")) 
```
Plot 6:
In this graph we examined the relationship between building type and sale price. Single-family homes and townhouses seemed to have comparable median sale prices, though the single-family homes did have a significantly higher number of more expensive outliers. The single-family homes also had a slightly lower minimum sale price, though this wider range is likely in part due to there being many more single family homes listed than townhomes and the greater variety of house styles that single-family homes have. 

```{r garage}

ggplot(testingdataset, aes(x=BldgType, y=GarageArea, fill=BldgType)) +
  geom_boxplot() +
  stat_summary(position = "dodge",
           fun=mean, geom='point', shape=20) +
  labs(title = "Central Tendencies of Garage Area based on Building Type",
       x = "Building Type",
       y = "Garage Area (Feet)",
       )
```
Plot 7:
In this graph we examined the relationship between building type and garage area. Interestingly, the two-family conversions seemed to have the greatest spread/interquartile range in terms of garage area, with all the other building types having, in comparison, relatively consistently sized garages. However, as in the previous graph, the single-family homes still have the greatest number of outliers on both ends.

```{r linear}

ggplot(testingdataset,aes(YearBuilt, SalePrice, fill = YrSold, color = YrSold)) +
  geom_point() +
  geom_smooth(method='lm') +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE, big.mark = ",")) +
     labs(title = "Prediction Model of SalePrice and Year Built",
       x = "Sale's Price ($)",
       y = "Lot Area (Feet)",
       )
```
Plot 8:
In this graph, we examined the relationship between the year the houses were built, the sales price, and the year they were sold. In general, we found that the later the houses were built, the more they were sold for – likely a function of inflation. The year sold, on the other hand, did not seem to have as much of a discernible relationship with the sales price.

```{r linear 2}

ggplot(testingdataset,aes(SalePrice, LotArea, fill = YrSold, color = YrSold)) +
  geom_point() +
  geom_smooth(method='lm') +
  scale_y_continuous(labels = function(x) format(x, big.mark = ",")) +
  scale_x_continuous(labels = function(x) format(x, scientific = FALSE, big.mark = ",")) +
    labs(title = "Prediction Model of SalePrice and Lot Area",
       x = "Sale's Price ($)",
       y = "Lot Area (Feet)",
       )
```
Plot 9:
In this graph, we examined the relationship between the sale price, lot area, and year sold. We found that as the sale price increased, the lot area would also increase, albeit at a relatively low rate. We also noticed that there were a fair number of outliers that had relatively average or slightly above-average sales prices, but significantly higher lot areas than comparably priced homes. These outliers likely represent farmland or rural lots in which the price per acre is significantly lower than the price in more suburban or urban areas. 


